\chapter{Preliminary Comments On Notes}

These notes were taken during lectures themselves, but have undergone significant editing afterwards by both myself and Paul. In some places this has resulted in me (Richie) adding completely new material that was not discussed during the course. This is mainly done for my own understanding on the background of some of the results used. Sections that contain a lot of unlectured material will be marked with an asterisk.

\mybox{
    \begin{center}
        The important results that appear in these section will be put in boxes like this.
    \end{center}
}

I will try not to rely too heavily on the details of these additional sections, and any calculations used later in the course I shall present again. This is done so that, in principle, the non-asterisked sections can be read in a self contained way (up to accepting the boxed results). The disclaimer is that I will use the notation from these sections (e.g. putting tildes on the charges associated to the conformal differential operators), so if any notation seems strange, the reader is requested to glance these sections for clarity.  

\badr 
    Other, non-asterisked, sections will also include small additions here and there and these will normally be included as additional remarks like this.\footnote{Some will also appear as footnotes.} 
\eadr

\br
    Within the asterisked sections I will just use `normal' remarks (i.e. not "Additional Remark"), like this.
\er     

Of course some of these additions will naturally be part of the text itself. 

All this additional material should be understood with caution as I may have misinterpreted results I've seen from places. Of course any errors etc in these parts are entirely my fault and should not reflect on the course itself. 